Towards a free/open-source universal-dependency treebank for Kazakh

### 2015-06-20 2015-turklang-kazdep/paper.tex
font size change
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60868 72bbbca6-d526-0410-a7d9-f06f51895060
add some eval stuffs
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@60869 72bbbca6-d526-0410-a7d9-f06f51895060

%\usepackage{times}
\setmainfont{Times New Roman}
\newfontfamily\udfont[Scale=MatchLowercase,Letters=SmallCaps]{Linux Libertine O}

@@

\cite{ballesteros15}, \cite{nivre07}

>>>>

%\usepackage{times}
\setmainfont{Times New Roman}
\newfontfamily\udfont[Scale=1.3,Letters=SmallCaps]{Linux Libertine O}

@@

In order to test the utility of the treebank in a real-world setting, we trained
and evaluated a number of models using the popular MaltParser tool \citep{nivre07}.
MaltParser is a toolkit for data-driven dependency parsing, it can learn a parsing
model from treebank data and apply this model to parse unseen sentences. The parser
has a large number of options and parameters that need to be optimised.
To select the best parser configuration we relied on
MaltOptimiser \citep{ballesteros15}. The optimiser recommended the \emph{covnonproj}
parsing algorithm.

As the treebank takes advantage of the new tokenisation standards in the CoNLL-U format,
and MaltParser only supports CoNLL-X, certain transformations were needed to perform
the experiments. The corpus was flattened with conjoined tokens receiving a dummy
surface form. The converted corpus is available alongside the original.\footnote{\url{removed for review}}

% LAS: 0.5529 [0.434 0.446 0.501 0.511 0.515 0.542 0.558 0.572 0.7 0.75]
% UAS: 0.7376 [0.658 0.669 0.675 0.684 0.694 0.723 0.751 0.776 0.825 0.921]

\begin{table}
  \centering
  \begin{tabular}{|l|r|r|}
    \hline
    \textbf{Features} & \textbf{LAS} & \textbf{UAS} \\
    \hline
     - & - & - \\
    \hline
  \end{tabular}
  \caption{Preliminary parsing results from MaltParser using different models}
  \label{table:eval}
\end{table}

To perform 10-fold cross validation we randomised the order of sentences in the corpus
and split it into 10 parts. In each iteration we held out one part for testing and used
the rest for training. We calculated the labelled-attachment score (LAS) and
unlabelled-attachment score (UAS) for each of the models.

The results we obtain for unlabelled attachment are similar to those obtained with similar 
sized treebanks, for example the Irish treebank of \cite{Lynn12}, who report an LAS of
63.3 and a UAS of 73.3 with the best model.
